DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-05 paper/main.tex
use hyperref package
reorg: add comparison section
Add draft abstract

%\usepackage[pdftex]{hyperref}
\usepackage{rotating,tabularx}

@@

\maketitle
\thispagestyle{empty}
\begin{abstract}
Abstract goes here.
\end{abstract}

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{related}
\input{conclusion}
%-------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{reference}
\end{document}

>>>>

\usepackage[pdftex]{hyperref}
\usepackage{rotating,tabularx}

@@

\maketitle
\thispagestyle{empty}
\begin{abstract}
In order to effectively research autonomous vehicles, a real-time capable platform is required. Such 
platforms can be hard to obtain, or build, as the necessary components can be expensive. In this paper, 
we present a low-cost alternative platform that utilizes a Raspberry Pi 3 Model B, along with a single 
external camera sensor, to perform all necessary self-driving operations. A convolutional neural network 
(CNN) is employed and trained with input from a human driver to navigate a custom made track. We display 
the real-time efficacy of our platform in experiments with varying amount of computational resources 
and/or intensive AI workloads. To gain a better understanding of our platform's potential, we compare it 
to other embedded computing platforms to determine which are suitable for autonomous driving research.
\end{abstract}

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{related}
\input{conclusion}
%-------------------------------------------------------------------------
\bibliographystyle{abbrv}
\bibliography{reference}

\appendix
\end{document}
